---
title: "Models"
---

```{r setup}
library(tidyverse)
library(modelr)
library(broom)


setwd("~/GitHub/welcome-to-the-tidyverse/04-Model")
library(readxl)
wages <- read_excel("wages.xlsx") %>% 
mutate(education = as.numeric(education))    #make education column read as numbers#
View(wages)


#Import wages here#

# Fall back in case you cannot load wages
# wages <- heights %>%
#   filter(income > 0) %>%
#   mutate(marital = as.character(marital),
#          sex = as.character(sex))
```

## Your Turn 1

* Change the working directory to `04-Models`. 
* Then import `wages.xlsx` as wages and *copy the code to your setup chunk*.
* Be sure to set NA: to NA.


## Your Turn 2

Fit the model on the slide and then examine the output. What does it look like?

```{r}

mod_e <- lm(log(income) ~ education, data = wages)
mod_e

mod_e %>% tidy()

mod_e %>% glance()

mod_e %>%  augment()
```

## Your Turn 3

Use a pipe to model `log(income)` against `height`. Then use broom and dplyr functions to extract:

1. The **coefficient estimates** and their related statistics 
2. The **adj.r.squared** and **p.value** for the overall model

```{r}
mod_h <- lm(log(income) ~ height, data = wages)
mod_h
mod_h %>% glance()
```


## Your Turn 4

Model `log(income)` against `education` and `height` and `sex`. Can you interpret the coefficients?

```{r}
mod_h <- lm(log(income) ~ education + height + sex, data = wages)
mod_h
mod_h %>%  tidy()
```

## Your Turn 5

Add `+ geom_smooth(method = lm)` to the code below. What happens?

```{r}
wages %>%
     ggplot(aes(x = height, y = log(income))) +
     geom_point(alpha = 0.1) +
  geom_smooth(method = lm)

```


## Your Turn 6

Use `add_predictions` to make the plot below.

```{r warning = FALSE, message = FALSE}

# In case you haven't made the ehs model
mod_ehs <- wages %>% lm(log(income) ~ education + height + sex, data = .)
mod_ehs <- wages %>% add_predictions(mod_ehs)
# Make plot here
ggplot(mod_ehs) +
  geom_line(aes(x=height, y=pred, color = sex)) +
            facet_wrap(~education)
```
```{r}
add_residuals(wages, mod_e, var="residual")
add_residuals(wages, mod_h, var="residual")
wages %>% spread_residuals(mod_e, mod_h)  
wages %>% gather_residuals(mod_e, mod_h)
```

***  

# Take Aways

* Use `glance()`, `tidy()`, and `augment()` from the **broom** package to return model values in a data frame.

* Use `add_predictions()` or `gather_predictions()` or `spread_predictions()` from the **modelr** package to visualize predictions.

* Use `add_residuals()` or `gather_residuals()` or `spread_residuals()` from the **modelr** package to visualize residuals.

