---
title: "DBI Example"
output: html_document
---

Note: This RMarkdown script will not knit because the connection settings are fake. It is a template you can use for other things.

```{r}
knitr::opts_chunk$set(echo = TRUE)
# DBI Example
library(DBI)
library(tidyverse)
```
# Credential Files

You should always store credentials and keys in a file as environmental variables! *Do not* hard code them into your scripts!

To create a renviron file type `usethis::edit_r_environ("project")` for a project specific file, or to edit your global environ file type `usethis::edit_r_environ()`. Global variable changes will load whenever you restart your R Session.

You must also check your drivers by opening ODBC Data Sources (64-bit) and look at the Drivers tab, anything with "SQL Server" in the Name will work to connect to the Data Warehouse. If you want, you can make this an environmental variable too.

```{r setup}
readRenviron(".renviron") # Remove the string if you are using your global profile.

# Set SQL Server Driver
driver <- "{ODBC Driver 17 for SQL Server}" # Set your Driver Name based off of the Name in ODBC Data Sources

# DB Connection String
con <- dbConnect(odbc::odbc(), driver = driver, server = "DEVSQL17\\CountyStat_DW", database = "HealthCare_DataWarehouse", UID = Sys.getenv("uid"), pwd = Sys.getenv("pwd"), Trusted_Connection= "yes")
```

# Build a SQL Query and load it

```{r sql}
# Build SQL Query
sql <- "Enter One of Today's Class SQL Queries Here"

# Get Query
query <- dbGetQuery(con, sql)
View(table)
```

```{r table}
# Get Table
table <- dbReadTable(con, SQL("ACHD.Health_SalesForce_Site"))
View(table)
```

## Disconnect from Database

```{r disconnect, echo=FALSE}
dbDisconnect(con)
```

# Oracle Connections

This connection method requires rJava, follow these [instructions](https://cimentadaj.github.io/blog/2018-05-25-installing-rjava-on-windows-10/installing-rjava-on-windows-10/) you likely won't be able to do this yourself and will need DIT to do this for you.

This would be necessary to install 

```{r oracle_setup}
library(RJDBC)

# Build the driver using JDBC
jdbcDriver <- JDBC(driverClass="oracle.jdbc.OracleDriver", classPath="ojdbc6.jar")

# Establish the connection
oracle <- dbConnect(jdbcDriver, "jdbc:oracle:thin:@//samedatabase:1522/schema", Sys.getenv("uid"), Sys.getenv("pwd"))
```

# Build a SQL Query and load it

```{r oracle}

# Build SQL Query
sql <- "SELECT *
FROM OracleDB.dbo.Table"

# Get Query
table <- dbGetQuery(oracle, sql)
```

## Disconnect from Database

```{r disconnect_oracle, echo=FALSE}
dbDisconnect(oracle)
```
